Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-03-22 Paper/Manuscript.tex
Move bibliography to the .bib file method

%\bibliography{ek80refs}

\begin{thebibliography}{39}
\def\enquote#1{``#1,''}
\def\plainquote#1{``#1''}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\dourl}[1]{\href{http://#1}{\nolinkurl{#1}}}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\noopsort}[1]{}
\providecommand{\switchargs}[2]{#2#1}
  \def\eatspace #1{#1}
\providecommand{\dodoi}[1]{doi: \href{http://dx.doi.org/#1}{\nolinkurl{#1}}}

\bibitem[{Barr \emph{et~al.}(2002)Barr, Coombs, Doonan, and
  McMillian}]{Barr2002Target}
\bibinfo{author}{Barr, R.}, \bibinfo{author}{Coombs, R.},
  \bibinfo{author}{Doonan, I.},  and \bibinfo{author}{McMillian, P.}
  (\textbf{\bibinfo{year}{2002}}). \enquote{\bibinfo{title}{Target
  identification of oreos and associated species}} \bibinfo{type}{Final
  {{Research Report}} for the {{Ministry}} of {{Fisheries Research Project
  OEO2000}}/{{01B}}, {{Objective}} 1} ,
  \dourl{fs.fish.govt.nz/Page.aspx?pk=113&dk=22653}, \bibinfo{note}{(Last
  viewed October 21, 2019)}.

\bibitem[{Bassett \emph{et~al.}(2018)Bassett, De~Robertis, and
  Wilson}]{bassettBroadbandEchosounderMeasurements2018}
\bibinfo{author}{Bassett, C.}, \bibinfo{author}{De~Robertis, A.},  and
  \bibinfo{author}{Wilson, C.~D.} (\textbf{\bibinfo{year}{2018}}).
  \enquote{\bibinfo{title}{Broadband echosounder measurements of the frequency
  response of fishes and euphausiids in the {{Gulf}} of {{Alaska}}}}
  \bibinfo{journal}{ICES Journal of Marine Science} \textbf{75}(3),
  \bibinfo{pages}{1131--1142}, \dodoi{10.1093/icesjms/fsx204}.

\bibitem[{Briseño-Avena \emph{et~al.}(2015)Briseño-Avena, Roberts, Franks,
  and Jaffe}]{Briseno-Avena2015ZOOPS}
\bibinfo{author}{Briseño-Avena, C.}, \bibinfo{author}{Roberts, P. L.~D.},
  \bibinfo{author}{Franks, P. J.~S.},  and \bibinfo{author}{Jaffe, J.~S.}
  (\textbf{\bibinfo{year}{2015}}).
  \enquote{\bibinfo{title}{{ZOOPS-O\textsuperscript{2}: A broadband echosounder
  with coordinated stereo optical imaging for observing plankton in situ}}}
  \bibinfo{journal}{Methods in Oceanography} \textbf{12},
  \bibinfo{pages}{36--54}, \dodoi{10.1016/j.mio.2015.07.001}.

\bibitem[{Burdic(1991)}]{burdic1991}
\bibinfo{author}{Burdic, W.~S.} (\textbf{\bibinfo{year}{1991}}).
  \emph{\bibinfo{title}{Underwater Acoustic System Analysis}}
  (\bibinfo{publisher}{{Prentice Hall}}).

\bibitem[{Chu and Stanton(1998)}]{Chu1998Application}
\bibinfo{author}{Chu, D.},  and \bibinfo{author}{Stanton, T.}
  (\textbf{\bibinfo{year}{1998}}). \enquote{\bibinfo{title}{{Application of
  pulse compression techniques to broadband acoustic scattering by live
  individual zooplankton}}} \bibinfo{journal}{The Journal of the Acoustical
  Society of America} \textbf{104}(1), \bibinfo{pages}{39–55},
  \dodoi{10.1121/1.424056}.

\bibitem[{Chu \emph{et~al.}(1992)Chu, Stanton, and Wiebe}]{chu1992}
\bibinfo{author}{Chu, D.}, \bibinfo{author}{Stanton, T.},  and
  \bibinfo{author}{Wiebe, P.} (\textbf{\bibinfo{year}{1992}}).
  \enquote{\bibinfo{title}{Frequency dependence of sound backscattering from
  live individual zooplankton}} \bibinfo{journal}{ICES Journal of Marine
  Science} \textbf{49}(1), \bibinfo{pages}{97--106},
  \dodoi{10.1093/icesjms/49.1.97}.

\bibitem[{Conti and Demer(2003)}]{Conti2003Wide-bandwidth}
\bibinfo{author}{Conti, S.~G.},  and \bibinfo{author}{Demer, D.~A.}
  (\textbf{\bibinfo{year}{2003}}). \enquote{\bibinfo{title}{{Wide-bandwidth
  acoustical characterization of anchovy and sardine from reverberation
  measurements in an echoic tank}}} \bibinfo{journal}{ICES Journal of Marine
  Science} \textbf{60}(3), \bibinfo{pages}{617--624},
  \dodoi{10.1016/S1054-3139(03)00056-0}.

\bibitem[{Cook and Bernfield(1967)}]{cook1967}
\bibinfo{author}{Cook, C.},  and \bibinfo{author}{Bernfield, M.}
  (\textbf{\bibinfo{year}{1967}}). \emph{\bibinfo{title}{Radar {{Signals}}:
  {{An Introduction}} to {{Theory}} and {{Application}}}}
  (\bibinfo{publisher}{{Academic Press, Inc.}}).

\bibitem[{Demer \emph{et~al.}(2015)Demer, Berger, Bernasconi, Boswell, Chu,
  Domokos, Dunford, F\"assler, Gauthier, Hufnagle, Jech, Bouffant,
  {Lebourges-Dhaussy}, Lurton, Macaulay, Perrot, Ryan, {Parker-Stetter},
  Stienessen, Weber, and Williamson}]{demerCalibrationAcousticInstruments2015}
\bibinfo{author}{Demer, D.~A.}, \bibinfo{author}{Berger, L.},
  \bibinfo{author}{Bernasconi, M.}, \bibinfo{author}{Boswell, K.~M.},
  \bibinfo{author}{Chu, D.}, \bibinfo{author}{Domokos, R.},
  \bibinfo{author}{Dunford, A.~J.}, \bibinfo{author}{F\"assler, S. M.~M.},
  \bibinfo{author}{Gauthier, S.}, \bibinfo{author}{Hufnagle, L.~T.},
  \bibinfo{author}{Jech, J.~M.}, \bibinfo{author}{Bouffant, N.},
  \bibinfo{author}{{Lebourges-Dhaussy}, A.}, \bibinfo{author}{Lurton, X.},
  \bibinfo{author}{Macaulay, G.~J.}, \bibinfo{author}{Perrot, Y.},
  \bibinfo{author}{Ryan, T.~E.}, \bibinfo{author}{{Parker-Stetter}, S.},
  \bibinfo{author}{Stienessen, S.}, \bibinfo{author}{Weber, T.~C.},  and
  \bibinfo{author}{Williamson, N.~J.} (\textbf{\bibinfo{year}{2015}}).
  \enquote{\bibinfo{title}{Calibration of acoustic instruments}}
  \bibinfo{type}{{{ICES Cooperative Research Report No}}. 326} ,
  \dodoi{10.17895/ices.pub.5494}.

\bibitem[{Denny and Simpson(1998)}]{dennyBroadbandAcousticFish1998}
\bibinfo{author}{Denny, G.},  and \bibinfo{author}{Simpson, P.}
  (\textbf{\bibinfo{year}{1998}}). \enquote{\bibinfo{title}{A broadband
  acoustic fish identification system}} \bibinfo{journal}{The Journal of the
  Acoustical Society of America} \textbf{103}(5), \bibinfo{pages}{3069--3069},
  \dodoi{10.1121/1.422851}.

\bibitem[{Ehrenberg(1979)}]{ehrenberg1979}
\bibinfo{author}{Ehrenberg, J.~E.} (\textbf{\bibinfo{year}{1979}}).
  \enquote{\bibinfo{title}{A comparative analysis of {\emph{in situ}} methods
  for directly measuring the acoustic target strength of individual fish}}
  \bibinfo{journal}{IEEE Journal of Oceanic Engineering} \textbf{4}(4),
  \bibinfo{pages}{141--152}, \dodoi{10.1109/JOE.1979.1145434}.

\bibitem[{Ehrenberg and Torkelson(2000)}]{ehrenbergFMSlideChirp2000}
\bibinfo{author}{Ehrenberg, J.~E.},  and \bibinfo{author}{Torkelson, T.~C.}
  (\textbf{\bibinfo{year}{2000}}). \enquote{\bibinfo{title}{{{FM}} slide
  (chirp) signals: A technique for significantly improving the signal-to-noise
  performance in hydroacoustics assessment systems}}
  \bibinfo{journal}{Fisheries Research} \textbf{47}, \bibinfo{pages}{193--199},
  \dodoi{10.1016/S0165-7836(00)00169-7}.

\bibitem[{Foote \emph{et~al.}(2005)Foote, Atkins, Francis, and
  Knutsen}]{Foote2005Measuring}
\bibinfo{author}{Foote, K.~G.}, \bibinfo{author}{Atkins, P.~R.},
  \bibinfo{author}{Francis, D. T.~I.},  and \bibinfo{author}{Knutsen, T.}
  (\textbf{\bibinfo{year}{2005}}). \enquote{\bibinfo{title}{{Measuring echo
  spectra of marine organisms over a wide bandwidth}}}
  \bibinfo{address}{Proceedings of the International Conference on Underwater Acoustic Measurements: Technologies and Results, Heraklion, Crete}.

\bibitem[{Forland \emph{et~al.}(2014)Forland, Hobæk, and
  Korneliussen}]{Forland2014Scattering}
\bibinfo{author}{Forland, T.~N.}, \bibinfo{author}{Hobæk, H.},  and
  \bibinfo{author}{Korneliussen, R.~J.} (\textbf{\bibinfo{year}{2014}}).
  \enquote{\bibinfo{title}{{Scattering properties of Atlantic mackerel over a
  wide frequency range}}} \bibinfo{journal}{ICES Journal of Marine Science}
  \textbf{71}(7), \bibinfo{pages}{1904--1912}, \dodoi{10.1093/icesjms/fsu045}.

\bibitem[{Gordon and Zedel(1998)}]{Gordon1998FishMASS}
\bibinfo{author}{Gordon, L.},  and \bibinfo{author}{Zedel, L.}
  (\textbf{\bibinfo{year}{1998}}). \enquote{\bibinfo{title}{{FishMASS: what can
  you do with a little bandwidth when you are watching fish?}}}
  \bibinfo{journal}{IEEE Seminar Digests} \textbf{1998}(227),
  \bibinfo{pages}{7}, \dodoi{10.1049/ic:19980186}.

\bibitem[{Hasan(1983)}]{hasan1983}
\bibinfo{author}{Hasan, T.} (\textbf{\bibinfo{year}{1983}}).
  \enquote{\bibinfo{title}{Complex demodulation: {{Some}} theory and
  applications}} in \emph{\bibinfo{booktitle}{Handbook of {{Statistics}}}},
  \bibinfo{volume}{\textbf{3}} (\bibinfo{publisher}{{Elsevier}}), pp.
  \bibinfo{pages}{125--156}, \dodoi{10.1016/S0169-7161(83)03009-6}.

\bibitem[{Hob\ae{}k and
  Forland(2013)}]{hobaekCharacterizationTargetSpheres2013}
\bibinfo{author}{Hob\ae{}k, H.},  and \bibinfo{author}{Forland, T.~N.}
  (\textbf{\bibinfo{year}{2013}}). \enquote{\bibinfo{title}{Characterization of
  {{Target Spheres}} for {{Broad}}-{{Band Calibration}} of {{Acoustic
  Systems}}}} \bibinfo{journal}{Acta Acustica united with Acustica}
  \textbf{99}(3), \bibinfo{pages}{465--476}, \dodoi{10.3813/AAA.918627}.

\bibitem[{Holliday and Pieper(1980)}]{holliday1980}
\bibinfo{author}{Holliday, D.~V.},  and \bibinfo{author}{Pieper, R.~E.}
  (\textbf{\bibinfo{year}{1980}}). \enquote{\bibinfo{title}{Volume scattering
  strengths and zooplankton distributions at acoustic frequencies between 0.5
  and 3 {{MHz}}}} \bibinfo{journal}{The Journal of the Acoustical Society of
  America} \textbf{67}(1), \bibinfo{pages}{135--146}, \dodoi{10.1121/1.384472}.

\bibitem[{Imaizumi \emph{et~al.}(2009)Imaizumi, Abe, Sawada, Matsuda, Akamatsu,
  Suga, Wang, Nishimori, Ogawa, Matsuo, and Ito}]{Imaizumi2009Detection}
\bibinfo{author}{Imaizumi, T.}, \bibinfo{author}{Abe, K.},
  \bibinfo{author}{Sawada, K.}, \bibinfo{author}{Matsuda, A.},
  \bibinfo{author}{Akamatsu, T.}, \bibinfo{author}{Suga, T.},
  \bibinfo{author}{Wang, Y.}, \bibinfo{author}{Nishimori, Y.},
  \bibinfo{author}{Ogawa, S.}, \bibinfo{author}{Matsuo, I.},  and
  \bibinfo{author}{Ito, M.} (\textbf{\bibinfo{year}{2009}}).
  \enquote{\bibinfo{title}{{Detection of in situ fish using broadband
  split-beam system}}} \bibinfo{journal}{Institute of Electronics, Information,
  and Communication Engineers, Tech. Rep. IEICE-US2009-36} \textbf{109}(180),
  \bibinfo{pages}{39--42}.

\bibitem[{Klauder \emph{et~al.}(1960)Klauder, Price, Darlington, and
  Albersheim}]{klauder1960}
\bibinfo{author}{Klauder, J.~R.}, \bibinfo{author}{Price, A.~C.},
  \bibinfo{author}{Darlington, S.},  and \bibinfo{author}{Albersheim, W.~J.}
  (\textbf{\bibinfo{year}{1960}}). \enquote{\bibinfo{title}{The theory and
  design of chirp radars}} \bibinfo{journal}{The Bell System Technical Journal}
  \textbf{39}(4), \bibinfo{pages}{745--808},
  \dodoi{10.1002/j.1538-7305.1960.tb03942.x}.

\bibitem[{Korneliussen(2010)}]{korneliussen2010}
\bibinfo{author}{Korneliussen, R.~J.} (\textbf{\bibinfo{year}{2010}}).
  \enquote{\bibinfo{title}{The acoustic idenification of {{Atlantic}}
  mackerel}} \bibinfo{journal}{ICES Journal of Marine Science} \textbf{67}(8),
  \bibinfo{pages}{1749--1758}, \dodoi{10.1093/icesjms/fsq052}.

\bibitem[{Korneliussen \emph{et~al.}(2018)Korneliussen, Berger, Campanlla,
  Dezhang, Demer, De~Robertis, Domokos, Doray, Fielding, F\"assler, Gauthier,
  Gastauer, Horne, Hutton, Iriarte, Jech, Kloser, Lawson, {Lebourges-Dhaussy},
  McQuinn, Pe\~na, Scoulding, Sakinan, Schaber, Taylor, and
  Thompson}]{korneliussen2018}
\bibinfo{author}{Korneliussen, R.~J.}, \bibinfo{author}{Berger, L.},
  \bibinfo{author}{Campanlla, F.}, \bibinfo{author}{Dezhang, C.},
  \bibinfo{author}{Demer, D.}, \bibinfo{author}{De~Robertis, A.},
  \bibinfo{author}{Domokos, R.}, \bibinfo{author}{Doray, M.},
  \bibinfo{author}{Fielding, S.}, \bibinfo{author}{F\"assler, S. M.~M.},
  \bibinfo{author}{Gauthier, S.}, \bibinfo{author}{Gastauer, S.},
  \bibinfo{author}{Horne, J.}, \bibinfo{author}{Hutton, B.},
  \bibinfo{author}{Iriarte, F.}, \bibinfo{author}{Jech, J.~M.},
  \bibinfo{author}{Kloser, R.}, \bibinfo{author}{Lawson, G.},
  \bibinfo{author}{{Lebourges-Dhaussy}, A.}, \bibinfo{author}{McQuinn, I.},
  \bibinfo{author}{Pe\~na, M.}, \bibinfo{author}{Scoulding, B.},
  \bibinfo{author}{Sakinan, S.}, \bibinfo{author}{Schaber, M.},
  \bibinfo{author}{Taylor, J.~C.},  and \bibinfo{author}{Thompson, C.~H.}
  (\textbf{\bibinfo{year}{2018}}). \enquote{\bibinfo{title}{Target
  classification}} \bibinfo{type}{ICES Cooperative Research Report}
  \bibinfo{number}{No. 344} , \dodoi{doi.org/10.17895/ices.pub.4567}.

\bibitem[{Korneliussen \emph{et~al.}(2016)Korneliussen, Heggelund, Macaulay,
  Patel, Johnsen, and Eliassen}]{Korneliussen2016Acoustic}
\bibinfo{author}{Korneliussen, R.~J.}, \bibinfo{author}{Heggelund, Y.},
  \bibinfo{author}{Macaulay, G.~J.}, \bibinfo{author}{Patel, D.},
  \bibinfo{author}{Johnsen, E.},  and \bibinfo{author}{Eliassen, I.~K.}
  (\textbf{\bibinfo{year}{2016}}). \enquote{\bibinfo{title}{{Acoustic
  identification of marine species using a feature library}}}
  \bibinfo{journal}{Methods in Oceanography} \textbf{17},
  \bibinfo{pages}{187--205}, \dodoi{10.1016/j.mio.2016.09.002}.

\bibitem[{Korneliussen and Ona(2002)}]{Korneliussen2002operational}
\bibinfo{author}{Korneliussen, R.~J.},  and \bibinfo{author}{Ona, E.}
  (\textbf{\bibinfo{year}{2002}}). \enquote{\bibinfo{title}{{An operational
  system for processing and visualizing multi-frequency acoustic data}}}
  \bibinfo{journal}{ICES Journal of Marine Science} \textbf{59}(2),
  \bibinfo{pages}{293--313}, \dodoi{10.1006/jmsc.2001.1168}.

\bibitem[{Lavery \emph{et~al.}(2017)Lavery, Bassett, Lawson, and Jech}]{lavery2017}
\bibinfo{author}{Lavery, A.~C.},  \bibinfo{author}{Bassett, C.},
  \bibinfo{author}{Lawson, G.~L.}, and \bibinfo{author}{Jech. J.~M.}
  (\textbf{\bibinfo{year}{2017}}). \enquote{\bibinfo{title}{{Exploiting signal 
  processing approaches for broadband echosounders}}} \bibinfo{journal}{ICES Journal
  of Marine Science} \textbf{74}(8), \bibinfo{pages}{2262--2275},
  \dodoi{10.1093/icesjms/fsx155}.

\bibitem[{Lunde and Korneliussen(2016)}]{lunde2016}
\bibinfo{author}{Lunde, P.},  and \bibinfo{author}{Korneliussen, R.~J.}
  (\textbf{\bibinfo{year}{2016}}). \enquote{\bibinfo{title}{Power-{{Budget
  Equations}} and {{Calibration Factors}} for {{Fish Abundance Estimation Using
  Scientific Echo Sounder}} and {{Sonar Systems}}}} \bibinfo{journal}{Journal
  of Marine Science and Engineering} \textbf{4}(3), \bibinfo{pages}{43},
  \dodoi{10.3390/jmse4030043}.

\bibitem[{MacLennan(1981)}]{maclennan1981}
\bibinfo{author}{MacLennan, D.~N.} (\textbf{\bibinfo{year}{1981}}).
  \enquote{\bibinfo{title}{The {{Theory}} of {{Solid Spheres}} as {{Sonar
  Calibration Targets}}}} \bibinfo{type}{Scottish {{Fisheries Research Report
  Number}} 22} .

\bibitem[{MacLennan \emph{et~al.}(2002)MacLennan, Fernandes, and
  Dalen}]{MacLennan2002consistent}
\bibinfo{author}{MacLennan, D.~N.}, \bibinfo{author}{Fernandes, P.},  and
  \bibinfo{author}{Dalen, J.} (\textbf{\bibinfo{year}{2002}}).
  \enquote{\bibinfo{title}{{A consistent approach to definitions and symbols in
  fisheries acoustics}}} \bibinfo{journal}{ICES Journal of Marine Science}
  \textbf{59}, \bibinfo{pages}{365--369}, \dodoi{10.1006/jmsc.2001.1158}.

\bibitem[{Simmonds \emph{et~al.}(1996)Simmonds, Armstrong, and
  Copland}]{Simmonds1996Species}
\bibinfo{author}{Simmonds, E.~J.}, \bibinfo{author}{Armstrong, F.},  and
  \bibinfo{author}{Copland, P.~J.} (\textbf{\bibinfo{year}{1996}}).
  \enquote{\bibinfo{title}{{Species identification using wideband backscatter
  with neural network and discriminant analysis}}} \bibinfo{journal}{ICES
  Journal of Marine Science} \textbf{53}(2), \bibinfo{pages}{189–195},
  \dodoi{10.1006/jmsc.1996.0021}.

\bibitem[{Simmonds and MacLennan(2005)}]{Simmonds2005Fisheries}
\bibinfo{author}{Simmonds, J.},  and \bibinfo{author}{MacLennan, D.}
  (\textbf{\bibinfo{year}{2005}}). \emph{\bibinfo{title}{{Fisheries Acoustics.
  Theory and Practice}}}, \bibinfo{edition}{2nd ed.}
  (\bibinfo{publisher}{Blackwell Science}, \bibinfo{address}{Oxford}).

\bibitem[{Skaret \emph{et~al.}(2020)Skaret, Johansen, Johnsen, Fall, Fiksen,
  Englund, Fauchald, Gj{\o}s{\ae}ter, Macaulay, and Johannesen}]{skaret2020}
\bibinfo{author}{Skaret, G.}, \bibinfo{author}{Johansen, G.~O.},
  \bibinfo{author}{Johnsen, E.}, \bibinfo{author}{Fall, J.},
  \bibinfo{author}{Fiksen, {\O}.}, \bibinfo{author}{Englund, G.},
  \bibinfo{author}{Fauchald, P.}, \bibinfo{author}{Gj{\o}s{\ae}ter, H.},
  \bibinfo{author}{Macaulay, G.~J.},  and \bibinfo{author}{Johannesen, E.}
  (\textbf{\bibinfo{year}{2020}}). \enquote{\bibinfo{title}{Diel vertical
  movements determine spatial interactions between cod, pelagic fish and krill
  on an {{Arctic}} shelf bank}} \bibinfo{journal}{Marine Ecology Progress
  Series} \textbf{638}, \bibinfo{pages}{13--23}, \dodoi{10.3354/meps13254}.

\bibitem[{Stanton and Chu(2008)}]{stanton2008}
\bibinfo{author}{Stanton, T.~K.},  and \bibinfo{author}{Chu, D.}
  (\textbf{\bibinfo{year}{2008}}). \enquote{\bibinfo{title}{Calibration of
  broadband active acoustic systems using a single standard spherical target}}
  \bibinfo{journal}{The Journal of the Acoustical Society of America}
  \textbf{124}(1), \bibinfo{pages}{128--136}, \dodoi{10.1121/1.2917387}.

\bibitem[{Stanton \emph{et~al.}(2010)Stanton, Chu, Jech, and
  Irish}]{Stanton2010New}
\bibinfo{author}{Stanton, T.~K.}, \bibinfo{author}{Chu, D.},
  \bibinfo{author}{Jech, J.~M.},  and \bibinfo{author}{Irish, J.~D.}
  (\textbf{\bibinfo{year}{2010}}). \enquote{\bibinfo{title}{{New broadband
  methods for resonance classification and high-resolution imagery of fish with
  swimbladders using a modified commercial broadband echosounder}}}
  \bibinfo{journal}{ICES Journal of Marine Science} \textbf{67}(2),
  \bibinfo{pages}{365--378}, \dodoi{10.1093/icesjms/fsp262}.

\bibitem[{Stanton \emph{et~al.}(2012)Stanton, Sellers, and
  Jech}]{Stanton2012Resonance}
\bibinfo{author}{Stanton, T.~K.}, \bibinfo{author}{Sellers, C.~J.},  and
  \bibinfo{author}{Jech, J.~M.} (\textbf{\bibinfo{year}{2012}}).
  \enquote{\bibinfo{title}{{Resonance classification of mixed assemblages of
  fish with swimbladders using a modified commercial broadband acoustic
  echosounder at 1–6 kHz}}} \bibinfo{journal}{Canadian Journal of Fisheries
  and Aquatic Sciences} \textbf{69}(5), \bibinfo{pages}{854--868},
  \dodoi{10.1139/f2012-013}.

\bibitem[{Traykovski \emph{et~al.}(1998)Traykovski, O'Driscoll, and
  McGhee}]{Traykovski1998Effect}
\bibinfo{author}{Traykovski, L.~M.}, \bibinfo{author}{O'Driscoll, R.},  and
  \bibinfo{author}{McGhee, D.} (\textbf{\bibinfo{year}{1998}}).
  \enquote{\bibinfo{title}{{Effect of orientation on broadband acoustic
  scattering of Antarctic krill \textit{Euphausia superba}: Implications for
  inverting zooplankton spectral acoustic signatures for angle of
  orientation}}} \bibinfo{journal}{The Journal of the Acoustical Society of
  America} \textbf{104}(4), \bibinfo{pages}{2121–2135},
  \dodoi{10.1121/1.423726}.

\bibitem[{Turin(1960)}]{turin1960}
\bibinfo{author}{Turin, G.} (\textbf{\bibinfo{year}{1960}}).
  \enquote{\bibinfo{title}{An introduction to matched filters}}
  \bibinfo{journal}{IRE Transactions on Information Theory} \textbf{6}(3),
  \bibinfo{pages}{311--329}, \dodoi{10.1109/TIT.1960.1057571}.

\bibitem[{Zakharia \emph{et~al.}(1989)Zakharia, Corgiatti, Joly, and
  Person}]{Zakharia1989Wide-band}
\bibinfo{author}{Zakharia, M.}, \bibinfo{author}{Corgiatti, J.},
  \bibinfo{author}{Joly, F.},  and \bibinfo{author}{Person, R.}
  (\textbf{\bibinfo{year}{1989}}). \enquote{\bibinfo{title}{{Wide-band sounder
  for fisheries}}} \bibinfo{journal}{Proceedings of the Institute of Acoustics}
  \textbf{11}, \bibinfo{pages}{274--281}.

\bibitem[{Zakharia \emph{et~al.}(1996)Zakharia, Magand, Hetroit, and
  Diner}]{Zakharia1996Wideband}
\bibinfo{author}{Zakharia, M.~E.}, \bibinfo{author}{Magand, F.},
  \bibinfo{author}{Hetroit, F.},  and \bibinfo{author}{Diner, N.}
  (\textbf{\bibinfo{year}{1996}}). \enquote{\bibinfo{title}{{Wideband sounder
  for fish species identification at sea}}} \bibinfo{journal}{ICES Journal of
  Marine Science} \textbf{53}, \bibinfo{pages}{203–208},
  \dodoi{10.1006/jmsc.1996.0023}.

\bibitem[{Zedel \emph{et~al.}(2003)Zedel, Knutsen, and
  Patro}]{Zedel2003Acoustic}
\bibinfo{author}{Zedel, L.}, \bibinfo{author}{Knutsen, T.},  and
  \bibinfo{author}{Patro, R.} (\textbf{\bibinfo{year}{2003}}).
  \enquote{\bibinfo{title}{{Acoustic Doppler current profiler observations of
  herring movement}}} \bibinfo{journal}{ICES Journal of Marine Science}
  \textbf{60}(4), \bibinfo{pages}{846--859},
  \dodoi{10.1016/s1054-3139(03)00067-5}.

\end{thebibliography}

>>>>

\bibliography{Reference_database}
